---
title: "Modelling the environment: from small-scale to global applications"
author: "Karline Soetaert and Thomas Petzoldt"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## UseR!2017 Conference, Brussels, 2017-07-04 14:00

* [Main conference web page](https://user2017.brussels/) conference tutorial. 
* [Abstract of the tutorial](https://www.user2017.brussels/uploads/Karline_Rtutorial2017.html)

## Download of the tutorial files

* as a ZIP-file from http://limno-live.hydro.tu-dresden.de/download

<!---
### Part 1: Introduction

* [Introduction and basics](1.0-basics/tutorial.pdf)
* [Forcing functions and events](2.1-forcing+events/desolve-forcing.html) 
* [Fitting parameters](2.2-fitting-parameters/index.html)

### Part 2: Special topics

* [Speeding up](2.4-compiled-code/desolve-compiled.html)
* [Web interfaces with shiny](2.5-desolve-shiny/desolve-shiny.html)
* [Complex models with rodeo](2.6-rodeo)
* [A multidimensional model](2.7-ocean)
--->

## Required software

Please have the following software installed on your laptop

### Recommended

* a laptop with Linux, Windows or MacOS
* a recent version of [**R**](https://cran.r-project.org/) (current is 3.4.0)
* a recent version of [**RStudio**](https://www.rstudio.com/products/rstudio/download/)
* packages **deSolve**, **FME**, **OceanView** and **shiny** (together with some dependencies, that are automatically installed)
* WiFi


### Optional

#### Execute the following function 

in **R** to install the packages above and some others that we use from time to time.

```{r eval=FALSE}
install.packages(c("deSolve", "marelac", "OceanView", "rootSolve", "bvpSolve",
 "deTestSet", "FME", "ReacTran", "marelac", "cOde", "scatterplot3d", "shiny",
 "AquaEnv", "rMarkdown", "devtools", "rodeo"))
```

#### Install the development tools

* Windows: https://cran.r-project.org/bin/windows/Rtools/
* Linux: 
    - Debian/Ubuntu `sudo apt-get r-base-dev`
    - Fedora `sudo yum install R`
* Mac: see https://cran.r-project.org/bin/macosx/    

### What are your most interested in?

The tentative plan of the tutorial can be found on https://www.user2017.brussels/uploads/Karline_Rtutorial2017.html
It consists of two parts, an introductory part and an outlook. You will see, that the outlook contains several options that cannot be covered in equal detail.

Please let us know what you are mostly interested in:

* how to make models more realistic by implementing forcing functions and events,
* how to implement complex models in an efficient way with package **rodeo**,
* how to speed up differential equation models (matrix formulation, code generators, parallel computing),
* how to create web-based model applications with **deSolve** and **shiny**.

Just send an email to us. karline.soetaert@nioz.nl and thomas.petzoldt@tu-dresden.de


## Links

* [Abstract of the Tutorial](https://www.user2017.brussels/uploads/Karline_Rtutorial2017.html)
* [useR!2017 Brussels](https://user2017.brussels/)
* package [deSolve](http://desolve.r-forge.r-project.org)
* mailig list  [R-SIG-DYNAMIC-MODELS](https://stat.ethz.ch/mailman/listinfo/r-sig-dynamic-models)
* this page: http://desolve.r-forge.r-project.org/user2017

See you in Brussels!

[Karline](http://www.marinebiology.ugent.be/node/78331) and [Thomas](https://tu-dresden.de/Members/thomas.petzoldt)

